\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Refactoring Extensions

Even after our greedy algorithm reduces the overall solution time to an $O(n^2)$, or polynomial time, there are still possible ways to improve it. One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together. As a result of such a method, we would reduce the problem to one with an $O(nlog(n))$, an algorithm that would easily scale to larger data sets.

>>>>

Even after our greedy algorithm reduces the overall solution time to an $O(n) = O(n^2k)$, or polynomial time, there are still possible ways to improve it. One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together. As a result of such a method, we would reduce the problem to one with an $O(n) = O(nlog(n))$, an algorithm that would easily scale to larger data sets.
